True versus apparent shapes of astrophysical bow shocks

### 2017-08-09 papers/Paper1/sec-quadrics-observations.tex
Finish description of MIPS/Herschel comparison

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
  \caption[]{Comparison of RSG/AGB arcs with OB star arcs.}
  \label{fig:herschel-compare-mipsgal}
\end{figure*}

@@

@@

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{figs/annotated-ll-arcs}
  \caption[]{Stationary bow shock arcs in the Orion Nebula.}
  \label{fig:ll-arcs}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
  \caption[]{Comparison of Orion with OB stars.}
  \label{fig:ll-compare-mipsgal}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
  \caption[]{Comparison of bow shock shapes between Herschel RSG/AGB
    arcs (large red symbols and hollow red contours) and MIPSGAL OB
    star arcs (small purple symbols and filled purple contours).
    Other details of the plots are as in
    Figs.~\ref{fig:mipsgal-shapes} and~\ref{fig:mipsgal-uncorrelated},
    except that the diagnostic plots are zoomed in slightly to show
    more detail, and a smaller KDE smoothing bandwidth of
    \(0.12 \times 0.08\) is used.}
  \label{fig:herschel-compare-mipsgal}
\end{figure*}

@@

Figure~\ref{fig:herschel-compare-mipsgal} compares the distributions
of bow shock shapes between the Herschel (RSG/AGB) and MIGSGAL (OB
star) samples.  The Anderson--Darling test gives a highly significant
difference between the \(R_{90}/R_0\) ratio distributions of the two
samples, but only a marginally significant difference between the
\(R_c/R_0\) ratio distributions (detailed results are shown in
Table~\ref{tab:big-p}).  The Herschel sources show considerably
smaller \(R_{90}\) ratio (median \(R_{90}/R_0 \approx 1.4\), implying bow
shock wings that are more closed than in the MIPSGAL sources (median
\(R_{90}/R_0 \approx 1.7\)).  For the radius of curvature ratio, there is
only a slight difference in average values: median
\(R_c/R_0 \approx 1.5\) for Herschel versus \(\approx 1.6\) for MIPSGAL, which is
not statistically significant (rank biserial \(p = 0.29\)).  On the
other hand, the dispersion in \(R_c/R_0\) is four times smaller for
the Herschel sample, which is marginally significant (Brown--Forsythe
\(p = 0.015\)).  In particular, the MIPSGAL sample shows a significant
minority of very flat-nosed shapes (\(R_c/R_0 > 2\)), but these are
absent in the Herschel sample.  The same can be seen directly by
comparing the RSG/AGB bow shock shapes in
Figures~\ref{fig:herschel-arc-fits}
and~\ref{fig:herschel-arc-fits-poor} with the representative OB bow
shocks of Figure~\ref{fig:mipsgal-shapes}b.  The MIPSGAL sources K489
and K123 have shapes that are similar to specific Herschel sources
(UU~Aur and R~Hya, respectively), while sources such as K447 (extreme
flat head) or K517 (extreme open wings) have no analog among the
Herschel sources.

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/annotated-ll-arcs}
  \caption[]{Stationary bow shock arcs in the Orion Nebula.}
  \label{fig:ll-arcs}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
  \caption[]{Comparison of Orion with OB stars.  Other details of the
    plots are as in Figs.~\ref{fig:mipsgal-shapes}
    and~\ref{fig:mipsgal-uncorrelated}, except that the diagnostic
    plots are zoomed out to encompass larger ratio values, and a
    larger KDE smoothing bandwidth of \(0.3 \times 0.2\) is used.}
  \label{fig:ll-compare-mipsgal}
\end{figure*}
